---
title: "Tht assay of 24 peptides"
output:   
  html_document: default
  pdf_document: default
widescreen: true

---


```{r, echo=FALSE,fig.height=150,fig.width=30,message=FALSE,warning=FALSE}
library(dplyr)
library(readODS)
library(reshape2)
library(ggplot2)
library(ggbeeswarm)
library(tidyverse)
library(DT)

peptydy <- read.csv("amyloid_heatmap.csv")
peptydy <- peptydy[1:(nrow(peptydy)-1),]
peptydy <- peptydy %>% mutate(match = ifelse(peptydy[["AmyLoad"]] == peptydy[["ThT"]], "yes", "no"))

peptydy <- peptydy %>% gather("method", "result", 2:4)

pep_order <- filter(peptydy, method == "AmyLoad") %>% arrange(result) %>%  pull(peptide) %>% as.character

peptydy[["peptide"]] <- factor(peptydy[["peptide"]], levels = pep_order)

ggplot(peptydy, aes(x = method, y = peptide, fill = result)) +
  geom_tile() +
  geom_tile(aes(fill = result), color = "white") +
  # scale_fill_manual(values=c("red", "lightgreen")) +
  scale_x_discrete(limits=c("AmyLoad","ThT","match")) +
  theme_bw()


overview <- read.csv("VU_peptides.csv")

```

## Overview

Created: 2018-11-09.

Parsed: `r Sys.Date()`.

## Aim 

Amylogram - amyloid prediction software, was used opn peptide sequences deposited in amyloid databases.

It found 24 peptides that had different annotation than prediction.

## Methods

For checking amyloidogenicity we used Tht array.

We diluted peptides in 100uL of 0.1M NaOH, gently mixed and neutralized pH to 7 using 50mM NaH2PO4.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
p
```


## Results overview

```{r, echo=FALSE, message=FALSE,warning=FALSE}
datatable(overview, extensions = 'Buttons', 
          filter = "top", rownames = FALSE, #style = "bootstrap",
          options = list(dom = "Brtip",
                         buttons = c("copy", "csv", "excel", "print")))
```
